% Syllabus
% Reporter of Decisions

\setcounter{page}{2}

193 Fed. Appx. 26, affirmed by an equally divided Court.

  \emph{Leonard J. Koerner} argued the cause for petitioner. With him on the briefs were \emph{Michael A. Cardozo, Edward F. X. Hart,} and \emph{Drake A. Colley.}

  \emph{Paul G. Gardephe} argued the cause for respondent. With him on the brief were \emph{Carrie A. Syme} and \emph{Alexis Gander Deise.}

  \emph{Deputy Solicitor General Garre} argued the cause for the United States as \emph{amicus curiae} urging affirmance. With him on the brief were \emph{Solicitor General Clement, Assistant Attorney General Kim, Jonathan L. Marcus, Diana K. Flynn, Lisa J. Stark,} and \emph{Kent D. Talbert.}[[*]]

\footnotetext[*]{Briefs of \emph{amici curiae} urging reversal were filed for the Council of the Great City Schools et al. by \emph{Julie Wright Halbert} and \emph{Pammela Quinn;} for the National School Boards Association et al. by \emph{Maree F. Sneed, John W. Borkowski, Audrey J. Anderson, Catherine E. Stetson, Jessica L. Ells\newpage worth, Francisco M. Negrón, Jr.,} and \emph{Naomi Gittins;} for the New York State School Boards Association by \emph{Jay Worona} and \emph{Pilar Sokol;} and for the U. S. Conference of Mayors et al. by \emph{Richard Ruda} and \emph{Donald B. Ayer.}

Briefs of \emph{amici curiae} urging affirmance were filed for Agudath Israel of America by \emph{David Zwiebel;} for Autism Speaks by \emph{Robert H. Pees} and \emph{Gary S. Mayerson;} for the Council of Parent Attorneys and Advocates et al. by \emph{Ankur J. Goel;} for the International Dyslexia Association, Inc., et al. by \emph{Paul M. Smith;} and for the National Disability Rights Network et al. by \emph{Beth S. Brinkmann, Seth M.
Galanter,} and \emph{Linda A. Arnsbarger.}}
