% Syllabus
% Reporter of Decisions

\setcounter{page}{248}

  Petitioner, a participant in a defined contribution pension plan, alleged that the plan administrator's failure to follow petitioner's investment directions ``depleted'' his interest in the plan by approximately \$150,000 and amounted to a breach of fiduciary duty under the Employee Retirement Income Security Act of 1974 (ERISA). The District Court granted respondents judgment on the pleadings, and the Fourth Circuit affirmed. Relying on \emph{Massachusetts Mutual Life Ins. Co.} v. \emph{Russell,} 473 U.~S. 134, the Circuit held that ERISA \S~502(a)(2) provides remedies only for entire plans, not for individuals.

\emph{Held:}

  Although \S~502(a)(2) does not provide a remedy for individual injuries distinct from plan injuries, it does authorize recovery for fiduciary breaches that impair the value of plan assets in a participant's individual account. Section 502(a)(2) provides for suits to enforce the liabilitycreating provisions of \S~409, concerning breaches of fiduciary duties that harm plans. The principal statutory duties imposed by \S~409 relate to the proper management, administration, and investment of plan assets, with an eye toward ensuring that the benefits authorized by the plan are ultimately paid to plan participants. The misconduct that petitioner alleges falls squarely within that category, unlike the misconduct in \emph{Russell.} There, the plaintiff received all of the benefits to which she was contractually entitled, but sought consequential damages arising from a delay in the processing of her claim. \emph{Russell}'s emphasis on protecting the ``entire plan'' reflects the fact that the disability plan in \emph{Russell,} as well as the typical pension plan at that time, promised participants a fixed benefit. Misconduct by such a plan's administrators will not affect an individual's entitlement to a defined benefit unless it creates or enhances the risk of default by the entire plan. For defined contribution plans, however, fiduciary misconduct need not threaten the entire plan's solvency to reduce benefits below the amount that participants would otherwise receive. Whether a fiduciary breach diminishes plan assets payable to all participants or only to particular individuals, it creates the kind of harms that concerned \S~409's draftsmen. Thus, \newpage \emph{Russell}'s ``entire plan'' references, which accurately reflect \S~409's operation in the defined benefit context, are beside the point in the defined contribution context. Pp. 252--256.

450 F. 3d 570, vacated and remanded.

  \textsc{Stevens,} J., delivered the opinion of the Court, in which \textsc{Souter, Ginsburg, Breyer,} and \textsc{Alito,} JJ., joined. \textsc{Roberts,} C. J., filed an opinion concurring in part and concurring in the judgment, in which \textsc{Kennedy,} J., joined, \emph{post,} p. 257. \textsc{Thomas,} J., filed an opinion concurring in the judgment, in which \textsc{Scalia,} J., joined, \emph{post,} p. 260.

  \emph{Peter K. Stris} argued the cause for petitioner. With him on the briefs were \emph{Brendan S. Maher, Jean-Claude André, Robert E. Hoskins,} and \emph{Shaun P. Martin.}

  \emph{Matthew D. Roberts} argued the cause for the United States as \emph{amicus curiae} urging reversal. With him on the brief were \emph{Solicitor General Clement, Deputy Solicitor General Kneedler, Jonathan L. Snare,} and \emph{Elizabeth Hopkins.}

  \emph{ThomasP.Gies} argued the cause for respondents. With him on the brief were \emph{Clifton Elgarten} and \emph{Ellen M. Dwyer.\\[[*]]

\footnotetext[*]{Briefs of \emph{amici curiae} urging reversal were filed for AARP by \emph{Mary Ellen Signorille, Jay E. Sushelsky,} and \emph{Melvin R. Radowitz;} for the Air Line Pilots Association, International, by \emph{Jani K. Rachelson;} for Eleven Law Professors by \emph{Paul A. Montuori} and \emph{Debra A. Davis;} for the Pension Rights Center by \emph{Marc I. Machiz} and \emph{David S. Preminger;} and for the Self Insurance Institute of America, Inc., by \emph{John E. Barry, Thomas W.} \emph{Brunner, Lawrence H. Mirel, Bryan B. Davenport,} and \emph{George J. Pantos.}

Briefs of \emph{amici curiae} urging affirmance were filed for the American Council of Life Insurers by \emph{Peter J. Rusthoven, Bart A. Karwath,} and \emph{Carl B. Wilkerson;} for the Chamber of Commerce of the United States of America et al. by \emph{Mark A. Casciari, Robin S. Conrad, Shane Brennan, Richard Whiting, Scott Talbott,} and \emph{Diane Soubly;} and for the ERISA Industry Committee by \emph{John M. Vine, Robert A. Long, Jr., Jeffrey G. Huvelle,} and \emph{Thomas L. Cubbage III.}

\emph{Jeffrey Greg Lewis} and \emph{Terisa E. Chaw} filed a brief for the National Employment Lawyers Association as \emph{amicus curiae.}}
