% Syllabus
% Reporter of Decisions

\setcounter{page}{440}

467 F. 3d 85, affirmed by an equally divided Court.

  \emph{Carter G. Phillips} argued the cause for petitioners. With him on
the briefs were \emph{Daniel E. Troy, Rebecca K. Wood, Eamon P. Joyce, Quin
M. Sorenson, David Klingsberg,} and \emph{Steven Glickstein.}

  \emph{Daryl Joseffer} argued the cause for the United States as \emph{amicus
curiae} urging reversal. With him on the brief were \emph{Solicitor General
Clement, Acting Assistant Attorney General Bucholtz, Deputy Solicitor
General Kneedler, Douglas N. Letter, Daniel Meron, Gerald F. Masoudi,}
and \emph{Eric M. Blumberg.}

  \emph{Allison M. Zieve} argued the cause for respondents. With her on the
brief were \emph{David R. Parker, Brian Wolfman, Scott L. Nelson, Theodore
Goldberg,} and \emph{David Bennet Rodes.\\[[*]]


^* Briefs of \emph{amici curiae} urging reversal were filed for the
Chamber of Commerce of the United States of America by \emph{Kenneth S.
Geller, David M. Gossett, Robin S. Conrad,} and \emph{Amar D. Sarwal;}
for the Generic Pharmaceutical Association by \emph{Jay P. Lefkowitz;}
for Pharmaceutical Research and Manufacturers of America by \emph{Bert W.
Rein;} and for the Product Liability Advisory Council by \emph{Robert N.
Weiner.}

  ^ Briefs of \emph{amici curiae} urging affirmance were filed for the
State of Kansas et al. by \emph{Paul J. Morrison,} Attorney General of
Kansas, \emph{Stephen . McAllister,} Solicitor General, and \emph{Jared S.
Maag,} Deputy Solicitor General, and by the Attorneys General for
their respective States as follows: \emph{Talis J. Colberg} of Alaska,
\emph{Terry Goddard} of Arizona, \emph{Bill McCollum} of Florida, \emph{Lawrence
G. Wasden} of Idaho, \emph{Lisa Madigan} of Illinois, \emph{Tom Miller} of
Iowa, \emph{Jack Conway} of Kentucky, \emph{Michael A. Cox} of Michigan,
\emph{Lori Swanson} of Minnesota, \emph{Jim Hood} of Mississippi, \emph{Jeremiah
W. (Jay) Nixon} of Missouri, \emph{Mike McGrath} of Montana, \emph{Catherine
Cortez Masto} of Nevada, \emph{Kelly A. Ayotte} of New Hampshire, \emph{Anne
Milgram} of New Jer\newpage sey, \emph{Gary K. King} of New Mexico, \emph{Andrew
M. Cuomo} of New York, \emph{Wayne Stenehjem} of North Dakota, \emph{Marc
Dann} of Ohio, \emph{W. A. Drew Edmondson} of Oklahoma, \emph{Hardy Myers}
of Oregon, \emph{Henry McMaster} of South Carolina, \emph{Lawrence E. Long}
of South Dakota, \emph{Mark L. Shurtleff} of Utah, \emph{William H. Sorrell}
of Vermont, \emph{Robert F. McDonnell} of Virginia, \emph{Robert M. Mc-Kenna}
of Washington, and \emph{Darrell V. McGraw, Jr.,} of West Virginia; for
AARP by \emph{David C. Vladeck} and \emph{Bruce Vignery;} for the American
Association for Justice by \emph{Francine A. Hochberg} and \emph{Kathleen Flynn
Peterson;} for the National Conference of State Legislatures et al. by
\emph{Richard Ruda} and \emph{Steven H. Goldblatt;} and for Public Justice,
P. C., by \emph{Leslie A. Brueckner, David J. Arkush,} and \emph{Arthur H.
Bryant.}

  ^ \emph{Eric G. Lasker, Daniel J. Popeo,} and \emph{Richard A. Samp} filed a
brief for the Washington Legal Foundation as \emph{amicus curiae.}
